On Secure Delegation of SampBQP with a Classical Client

### 2020-02-09 blind.tex
Combine evk into pk and resolve other simple notes

	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cPSamp{1}$.
	\begin{enumerate}
		\item The verifier generates $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, where $d$ is the depth of the circuit corresponding to $\cPSamp{1}(x)$.
			It then generates and sends $ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$ to the prover.
			It also sends $evk$ to the prover.
		\item The prover homomorphically evaluates $\cPSamp{1}$ on input $ct_x$, generating $\sigma\leftarrow\mathsf{QHE.Eval}_{evk}(\cPSamp{1}, ct_x)$.
			It sends $\sigma$ to the verifier qubit-by-qubit.
		\item The verifier generates $\Lambda\leftarrow\cVSamp{2}(x)$,
			$\Lambda'\leftarrow\cM_\QHE$,
			$ct_w\leftarrow\Lambda'(\sigma)$,
			$w\leftarrow\widehat{\mathsf{QHE.Dec}_{sk}}(ct_w)$,
			and $o\leftarrow\cVSamp{3}(x, \Lambda, w)$.
			It outputs $o$.
	\end{enumerate}
\end{protocol}

>>>>

	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cPSamp{1}$.
	\begin{enumerate}
		\item The verifier generates $(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, where $d$ is the depth of the circuit corresponding to $\cPSamp{1}(x)$.
			It then generates and sends $ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$ to the prover.
			It also sends $pk$ to the prover.
		\item The prover homomorphically evaluates $\cPSamp{1}$ on input $ct_x$, generating $\sigma\leftarrow\QEval_{pk}(\cPSamp{1}, ct_x)$.
			It sends $\sigma$ to the verifier qubit-by-qubit.
		\item The verifier generates $\Lambda\leftarrow\cVSamp{2}(x)$,
			$\Lambda'\leftarrow\cM_\QHE$,
			$ct_w\leftarrow\Lambda'(\sigma)$,
			$w\leftarrow\widehat{\mathsf{QHE.Dec}_{sk}}(ct_w)$,
			and $o\leftarrow\cVSamp{3}(x, \Lambda, w)$.
			It outputs $o$.
	\end{enumerate}
\end{protocol}

### 2020-02-09 bqp.tex
Combine evk into pk and resolve other simple notes

This is a one-message $\QPIP_1$ protocol $\PiMF$ with only $X$ and $Z$ measurement for deciding a $\BQP$ language $L$.
Roughly, on input $x\in\set{0,1}^n$, the prover sends a $m$-qubit certificate state $\rho$ to the verifier qubit-by-qubit.
The verifier samples a product measurement \Ethan{for consistency, ``measurement basis choice"} $\Lambda$ of $X$ and $Z$s according to a certain distribution, and applies it to $\rho$.
The verifier then, using the measurement results, decides whether to accept or reject.

\begin{protocol}{1-message $\QPIP_1$ protocol $\PiMF = (\PMF, \VMF)$ for $\BQP$ language $L$}
	\label{proto:BQP}
	Common input: $x\in\set{0,1}^n$. 
	\begin{enumerate}
		\item The prover generates a certificate state $\rho\leftarrow\cPMF{1}(x)$ and sends $\rho$ to the verifier qubit-by-qubit. \Ethan{Say it's $m$ qubits}
		\item The verifier generates $\Lambda \leftarrow \cVMF{2}(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$;
			each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement.
			It applies $\Lambda$ to $\rho$ qubit-by-qubit.
			Let $w \in \set{0,1}^m$ denote the measurement outcome.
			It verifies the measurement outcome and produces a decision $o\leftarrow\cVMF{3}(x, \Lambda, w)$ where $o\in\set{acc, rej}$ and $\cVMF{3}$ is a classical polynomial-time algorithm.
	\end{enumerate}
\end{protocol}
\begin{thm}
    \Ethan{Add reference}
    $\PiMF$ has negligible completeness and soundness.
\end{thm}

@@

\Ethan{TODO PROOFREAD ME}
\begin{thm}
	\label{decodeMeasureOrder}
	Let $n\in\bbN$.
	Let $m\in\bbN$ be the length of the ciphertexts under $\mathsf{QHE}$ corresponding to plaintexts of length $n$. \Ethan{$m$ isn't well-defined this way; missing security param. and depth param.}

	\Ethan{Keygen here}

	There exists efficient classical poly-time algorithms $\cM_\QHE$ and $\widehat{\mathsf{QHE.Dec}}$ s.t.
	for all $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_n$ where each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement:
	$$\cM_\QHE(\Lambda)=\Lambda'=\Lambda'_1\otimes\ldots\otimes\Lambda'_m$$
	where each $\Lambda_i'$ is a single-qubit $X$ or $Z$ measurement, and
	$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
\end{thm}
\begin{prf}
	This is a proof by construction.
	We require $\Lambda'$ and $\widehat{\mathsf{QHE.Dec}}$ such that $\forall\sigma=(X^xZ^z\rho Z^zX^x, c_{x,z})$,
	$$\Lambda\circ\mathsf{QHE.Dec}(\sigma)=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'(\sigma)$$
	Clearly,
	$$\Lambda\circ\mathsf{QHE.Dec}(\sigma)=\Lambda(\rho)$$

@@

	\begin{enumerate}
		\item The verifier generates $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, where $d$ is the depth of the circuit corresponding to $\cPMF{1}(x)$.
			It then generates and sends $ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$ to the prover.
			It also sends $evk$ to the prover.
		\item The prover homomorphically evaluates $\cPMF{1}$ on input $ct_x$, generating $\sigma\leftarrow\cPblind{1}(evk, ct_x)=\mathsf{QHE.Eval}_{evk}(\cPMF{1}, ct_x)$.
			It sends $\sigma$ to the verifier qubit-by-qubit.
		\item The verifier generates $\Lambda\leftarrow\cVMF{2}(x)$,
			$\Lambda'\leftarrow\cM_\QHE(\Lambda)$,
			$ct_w\leftarrow\Lambda'(\sigma)$,
			$w\leftarrow\widehat{\mathsf{QHE.Dec}_{sk}}(ct_w)$,
			and $o\leftarrow\cVMF{3}(x, \Lambda, w)$.
			It outputs $o$.
	\end{enumerate}
\end{protocol}

\begin{thm}
	\label{thm:BlindBQP}
	$\Piblind$ has negligible completeness and soundness, and is blind.
\end{thm}
\begin{prf}
	The completeness follows by inspection.
	For blindness, the only thing the prover sees is $c$ and $evk$, so it follows directly from $\mathsf{QHE}$'s security.

@@

	We define $\PMFstar$ to first generate
	$(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$
	and
	$y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$
	It then sends $ct_x$ and $evk$ to $\Pblindstar$ \Ethan{Just run it, don't send it} and gets $\sigma$ back.
	Finally, it decrypts
	$\rho\leftarrow\mathsf{QHE.Dec}_{sk}(\sigma)$
	and sends it to $\VMF$ qubit-by-qubit.

	We now prove that $\PMFstar$ in fact violates the soundness of $\PiMF$.
	Let $\cP_\blind^*$ denote the action $\Pblindstar$ takes to produce $\sigma$ from $ct_x$.
	Consider the experiment corresponding to $(\Vblind, \Pblindstar)$:
	$$(pk, sk, evk)\leftarrow\QGen(1^n, 1^d)$$
	$$ct_x\leftarrow\QEnc_{pk}(x)$$
	$$\sigma\leftarrow\cP_\blind^*(ct_x, evk)$$
	$$\Lambda\leftarrow\cVMF{2}(x)$$
	$$\Lambda'\leftarrow\cM_\QHE(\Lambda)$$
	$$ct_w\leftarrow\Lambda'(\sigma)$$
	$$w\leftarrow\widehat{\QDec_{sk}}(ct_w)$$
	$$o\leftarrow\cVMF(x, \Lambda, w)$$

	Compare it with the experiment corresponding to $\PMFstar$:
	$$(pk, sk, evk)\leftarrow\QGen(1^n, 1^d)$$
	$$ct_x\leftarrow\QEnc_{pk}(x)$$
	$$\sigma\leftarrow\cP_\blind^*(ct_x, evk)$$
	$$\Lambda\leftarrow\cVMF{2}(x)$$
	$$\rho\leftarrow\QDec_{sk}(\sigma)$$
	$$w\leftarrow\Lambda(\rho)$$
	$$o\leftarrow\cVMF(x, \Lambda, w)$$

@@

\begin{protocol}{Blind $\QPIP_0$ protocol $\Pibz$ for $BQP$ language $L$}
	\label{proto:QPIP0BQP}
	\begin{enumerate}
		\item The verifier generates $\Lambda, \Lambda', pk, sk, evk, ct_x$ the same way as in \cref{proto:BlindBQP}. \Ethan{Need more notation? But how?}
			Then, using $\Lambda'$, it generates $k, td$.
			It sends $k, evk, ct_x$ to the prover.
		\item The prover, on inputs $k, evk, ct_x$, generates classical ``commitment" $y$ and internal state $\ket{st}$.
			It sends $y$ to the verifier.
		\item The verifier sends the prover a public coin $c\in\set{0,1}$.
		\item The prover, on inputs $c$ and $\ket{st}$, generates classical $a$ and sends it to the verifier.
		\item The verifier, on inputs $k, td, y, c, a, sk$, generates and outputs either $acc$ or $rej$.
	\end{enumerate}
\end{protocol}

>>>>

This is a one-message $\QPIP_1$ protocol $\PiMF$ with only $X$ and $Z$ measurement for deciding a $\BQP$ language $L$.
Roughly, on input $x\in\set{0,1}^n$, the prover sends a certificate state $\rho$ to the verifier qubit-by-qubit.
The verifier samples a measurement basis choice $\Lambda$ according to a certain distribution, and applies it to $\rho$.
The verifier then, using the measurement results, decides whether to accept or reject.

\begin{protocol}{1-message $\QPIP_1$ protocol $\PiMF = (\PMF, \VMF)$ for $\BQP$ language $L$}
	\label{proto:BQP}
	Common input: $x\in\set{0,1}^n$. 
	\begin{enumerate}
		\item The prover generates a $m$-qubit certificate state $\rho\leftarrow\cPMF{1}(x)$ and sends $\rho$ to the verifier qubit-by-qubit.
		\item The verifier generates $\Lambda \leftarrow \cVMF{2}(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$;
			each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement.
			It applies $\Lambda$ to $\rho$ qubit-by-qubit.
			Let $w \in \set{0,1}^m$ denote the measurement outcome.
			It verifies the measurement outcome and produces a decision $o\leftarrow\cVMF{3}(x, \Lambda, w)$ where $o\in\set{acc, rej}$ and $\cVMF{3}$ is a classical polynomial-time algorithm.
	\end{enumerate}
\end{protocol}
\begin{thm}[from \cite{FOCS:Mahadev18a, mf16}]
    $\PiMF$ has negligible completeness and soundness.
\end{thm}

@@

\begin{thm}
	\label{decodeMeasureOrder}
	Let $n, L\in\bbN$.
	Let $(pk, sk)\leftarrow\QGen(1^n, 1^L)$
	Let $m=\poly(n)$ be the length of the ciphertexts under $\mathsf{QHE}$ corresponding to plaintexts of length $n$.

	There exists efficient classical poly-time algorithms $\cM_\QHE$ and $\widehat{\QDec_{sk}}$ s.t.
	for all $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_n$ where each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement:
	$$\cM_\QHE(\Lambda)=\Lambda'=\Lambda'_1\otimes\ldots\otimes\Lambda'_m$$
	where each $\Lambda_i'$ is a single-qubit $X$ or $Z$ measurement, and
	$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
\end{thm}
\begin{prf}
	This is a proof by construction.
	We require $\Lambda'$ and $\widehat{\mathsf{QHE.Dec}}$ such that $\forall\sigma=(X^xZ^z\rho Z^zX^x, c_{x,z})$,
	$$\Lambda\circ\mathsf{QHE.Dec}(\sigma)=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'(\sigma)$$
	Clearly,
	$$\Lambda\circ\mathsf{QHE.Dec}(\sigma)=\Lambda(\rho)$$

@@

	\begin{enumerate}
		\item The verifier generates $(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, where $d$ is the depth of the circuit corresponding to $\cPMF{1}(x)$.
			It then generates and sends $ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$ to the prover.
			It also sends $pk$ to the prover.
		\item The prover homomorphically evaluates $\cPMF{1}$ on input $ct_x$, generating $\sigma\leftarrow\cPblind{1}(pk, ct_x)=\QEval_{pk}(\cPMF{1}, ct_x)$.
			It sends $\sigma$ to the verifier qubit-by-qubit.
		\item The verifier generates $\Lambda\leftarrow\cVMF{2}(x)$,
			$\Lambda'\leftarrow\cM_\QHE(\Lambda)$,
			$ct_w\leftarrow\Lambda'(\sigma)$,
			$w\leftarrow\widehat{\mathsf{QHE.Dec}_{sk}}(ct_w)$,
			and $o\leftarrow\cVMF{3}(x, \Lambda, w)$.
			It outputs $o$.
	\end{enumerate}
\end{protocol}

\begin{thm}
	\label{thm:BlindBQP}
	$\Piblind$ has negligible completeness and soundness, and is blind.
\end{thm}
\begin{prf}
	The completeness follows by inspection.
	For blindness, the only thing the prover sees is $c$ and $pk$, so it follows directly from $\mathsf{QHE}$'s security.

@@

	We define $\PMFstar$ to first generate
	$(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$
	and
	$y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$
	It then sends $ct_x$ and $pk$ to $\Pblindstar$ \Ethan{Just run it, don't send it} and gets $\sigma$ back.
	Finally, it decrypts
	$\rho\leftarrow\mathsf{QHE.Dec}_{sk}(\sigma)$
	and sends it to $\VMF$ qubit-by-qubit.

	We now prove that $\PMFstar$ in fact violates the soundness of $\PiMF$.
	Let $\cP_\blind^*$ denote the action $\Pblindstar$ takes to produce $\sigma$ from $ct_x$.

	Observe the experiments $A$ and $B$ \Ethan{TODO} are identical except...

@@

\begin{protocol}{Blind $\QPIP_0$ protocol $\Pibz$ for $BQP$ language $L$}
	\label{proto:QPIP0BQP}
	\begin{enumerate}
		\item The verifier generates $\Lambda, \Lambda', pk, sk, ct_x$ the same way as in \cref{proto:BlindBQP}. \Ethan{Need more notation? But how?}
			Then, using $\Lambda'$, it generates $k, td$.
			It sends $k, pk, ct_x$ to the prover.
		\item The prover, on inputs $k, pk, ct_x$, generates classical ``commitment" $y$ and internal state $\ket{st}$.
			It sends $y$ to the verifier.
		\item The verifier sends the prover a public coin $c\in\set{0,1}$.
		\item The prover, on inputs $c$ and $\ket{st}$, generates classical $a$ and sends it to the verifier.
		\item The verifier, on inputs $k, td, y, c, a, sk$, generates and outputs either $acc$ or $rej$.
	\end{enumerate}
\end{protocol}

### 2020-02-09 preliminaries.tex
Combine evk into pk and resolve other simple notes

We use the quantum fully homomorphic encryption scheme given in \cite{mahadev_qfhe} which is compatible with our use of a classical client. We start by presenting the interface of a homomorphic encryption scheme:
\begin{dfn}
	A leveled homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{HE.Keygen}(1^\lambda, 1^L)\rightarrow(pk, evk, sk)$
		\item $\mathsf{HE.Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{HE.Dec}_{sk}(c)\rightarrow \mu^*$
		\item $\mathsf{HE.Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}

$\mathsf{HE}$ also satisfies, with overwhelming probability in $\lambda$, that
$$\mathsf{HE.Dec}_{sk}(\mathsf{HE.Eval}_{evk}(f, c_1, \ldots, c_l)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$
where $f$ is specified by a circuit of depth at most $L$.

@@

\begin{dfn}
	A FHE scheme $\mathsf{HE}$ is IND-CPA secure if, for any polynomial time adversary $\cA$, there exists a negligible function $\mu(\cdot)$ such that
	$$\abs{Pr[\cA(pk, evk, \mathsf{HE.Enc}_{pk}(0))=1]-Pr[\cA(pk, evk, \mathsf{HE.Enc}_{pk}(1))=1]}=\mu(\lambda)$$
	where $(pk, evk, sk)\leftarrow\mathsf{QHE.Keygen}(1^\lambda)$
\end{dfn}

The quantum homomorphic encryption scheme $\mathsf{QHE}$ from \cite{mahadev_qfhe} has additional properties that facilitates the use of a classical clients:
\begin{itemize}
	\item $\mathsf{QHE.Keygen}$ can be done classically.
	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
	\item Its ciphertext takes the form $(X^xZ^z\rho Z^zX^x, c_{x, z})$, where $\rho$ is the plaintext and $c_{x, z}$ is a ciphertext that decodes to $(x, z)$ under a certain classical homomorphic encryption scheme.
\end{itemize}

As we will see, if a given protocol has classical inputs and uses only $X$ and $Z$ measurements, then $\mathsf{QHE}$ can be used as a compiler to achieve blindness.

>>>>

We use the quantum fully homomorphic encryption scheme given in \cite{mahadev_qfhe} which is compatible with our use of a classical client. We start by presenting the interface of a homomorphic encryption scheme:
\begin{dfn}
	A leveled homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{HE.Keygen}(1^\lambda, 1^L)\rightarrow(pk, sk)$
		\item $\mathsf{HE.Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{HE.Dec}_{sk}(c)\rightarrow \mu^*$
		\item $\mathsf{HE.Eval}_{pk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}

$\mathsf{HE}$ also satisfies, with overwhelming probability in $\lambda$, that
$$\mathsf{HE.Dec}_{sk}(\mathsf{HE.Eval}_{pk}(f, c_1, \ldots, c_l)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$
where $f$ is specified by a circuit of depth at most $L$.

@@

\begin{dfn}
	A FHE scheme $\mathsf{HE}$ is IND-CPA secure if, for any polynomial time adversary $\cA$, there exists a negligible function $\mu(\cdot)$ such that
	$$\abs{Pr[\cA(pk, \mathsf{HE.Enc}_{pk}(0))=1]-Pr[\cA(pk, \mathsf{HE.Enc}_{pk}(1))=1]}=\mu(\lambda)$$
	where $(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^\lambda)$
\end{dfn}

The quantum homomorphic encryption scheme $\mathsf{QHE}$ from \cite{mahadev_qfhe} has additional properties that facilitates the use of a classical clients:
\begin{itemize}
	\item $\QGen$ can be done classically.
	\item In the case where the plaintext is classical, $\QEnc$ can be done classically.
	\item Its ciphertext takes the form $(X^xZ^z\rho Z^zX^x, c_{x, z})$, where $\rho$ is the plaintext and $c_{x, z}$ is a ciphertext that decodes to $(x, z)$ under a certain classical homomorphic encryption scheme.
\end{itemize}

As we will see, if a given protocol has classical inputs and uses only $X$ and $Z$ measurements, then $\QHE$ can be used as a compiler to achieve blindness.
